---
title: "Infographics Profound"
output:
  html_document:
    keep_md: yes
---


Aim: Create infoplots from profound database.

## Import data and libraries

First we import the data.

```{r}
#Load data: replace with your dropbox folder path
file_db = '/home/trashtos/Dropbox/Participants/OtherTables/list.csv'
file_coord = '/home/trashtos/Dropbox/Participants/OtherTables/coordinadesCountries.csv'
db = read.csv(file_db, header = TRUE, sep=",") 
coord = read.csv(file_coord, header = TRUE, sep=",") 
```

Load libraries require for plotting.

```{r}
library(plyr)
library(ggplot2)
library(ggmap)
library(rworldmap)
library(rworldxtra)
library(reshape2)
```


## Bar plots

#### Using ggplot

Create a bar plot for gender by country.

```{r, fig.height=8, fig.width=12, dpi = 144}
# summarise data
countMembersGender<- ddply(db,.(Country, Gender),summarise,count=length(Country))
# add acronyms
df = merge(countMembersGender, coord, by="Country")
# plot
a <- ggplot(df, aes(x = Acronym, y = count, fill = Gender)) +   labs(x = NULL, y = "Number of participants",  fill = NULL) + ggtitle("Participantsin the COST Profound action: gender") + 
    theme(
    axis.text = element_text(color='grey50'),
    #axis.line = element_line(color='grey10'),
    #legend.key = element_rect(fill = "navy"),
    legend.background = element_rect(fill = "white"),
    #legend.position = c(0.14, 0.80),
    panel.grid.major = element_line(colour = "white"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(fill = NA, colour = "black", size = 0.2),
    panel.background = element_rect(fill = 'white')
    )
b <- a + geom_bar(stat = "identity", position = "stack")
b
```


Create a bar plot for ESR by country:

```{r , fig.height=8, fig.width=12, dpi = 144}
# summarise data
countMembersESR<- ddply(db,.(Country, Early.Stage.Researcher ),summarise,count=length(Country))
# add acronyms
df = merge(countMembersESR, coord, by="Country")
df$Early.Stage.Researcher<-ifelse(df$Early.Stage.Researcher=='Yes','ESR','Non-ESR') 

# plot wit
a <- ggplot(df, aes(x = Acronym, y = count, fill = Early.Stage.Researcher)) +   labs(x = NULL, y = "Number of participants",  fill = NULL) + ggtitle("Participants in the COST Profound Action:  ESR") +
    theme(
    axis.text = element_text(color='grey50'),
    #axis.line = element_line(color='grey10'),
    #legend.key = element_rect(fill = "navy"),
    legend.background = element_rect(fill = "white"),
    #legend.position = c(0.14, 0.80),
    panel.grid.major = element_line(colour = "white"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(fill = NA, colour = "black", size = 0.2),
    panel.background = element_rect(fill = 'white')
    )
    
b <- a + geom_bar(stat = "identity", position = "stack")
b

# Try some other options
  ## Stacked bars
ba <-  a + geom_bar(stat = "identity", position = "stack")+ scale_fill_brewer()
ba

baa <-  a + geom_bar(stat = "identity", position = "stack")+ scale_fill_grey()
baa

  ## Adjacent bars
c<- a + geom_bar(stat = "identity", position="dodge") 
c

d<- a + geom_bar(stat = "identity", position="dodge") + facet_grid(. ~ Early.Stage.Researcher)
d

```

## Simple Bar Plots


Create a bar plot for gender by country.

```{r , fig.height=8, fig.width=12, dpi = 144 }
# Stacked Bar Plot with Colors and Legend
# summarise data
countMembers<- ddply(db,.(Country),summarise,count=length(Country))
# add acronyms
df = merge(db, coord, by="Country")
# prepare table
counts = table(df$Acronym)
par(las=1)
barplot(counts  )

# summarise data
#countMembersGender<- ddply(db,.(Country, Gender),summarise,count=length(Country))
# add acronyms
#df = merge(countMembersGender, coord, by="Country")
#
#barplot(df$counts, besides=TRUE  )



```



## Map of Europe with participants

Create a map with participants in the action. I plot the participants on the capital city of the country.

```{r , fig.height=8, fig.width=12, dpi = 144 }
# summarise data
countMembers <- ddply(db,.(Country),summarise,count=length(Country))
# add acronyms
df = merge(countMembers, coord, by="Country")
# Option 1: plot proportional circles
map <- get_map(location = 'europe', zoom=4, color ="bw")
mapPoints <- ggmap(map) +   geom_point(colour = "blue", aes(x = Lon, y = Lat, size=count), data = df, alpha = .5)
mapPointsLegend <- mapPoints  + scale_size_area(breaks = c(5, 10, 15, 20, 25, 30, 35) , labels = c(5, 10, 15, 20, 25, 30, 35), name = "Participants")
mapPointsLegend

# Option 2: plot bars
df<-rename(df, c("count"="Participants"))
mapBars(df , nameX="Lon", nameY="Lat",nameZs='Participants', zColours='indianred2', barWidth = 1, barOrient = 'vert', barRelative = FALSE, ratio = 1, mapRegion='europe',addCatLegend = TRUE, addSizeLegend = TRUE, symbolSize = 3 , maxZVal=30, xlim=NA, ylim=NA, oceanCol = "white", landCol = "grey60",borderCol = "white", add=FALSE, main='', lwd=0.5, lwdSymbols=1)  
```


Create a map with participants in the action using pie charts and stacked bars to represent male/female and ESR/nonESR. I plot the participants on the capital city of the country.

```{r , fig.height=10, fig.width=12, dpi = 144 }
# summarise data
countMembersESR<- ddply(db,.(Country, Early.Stage.Researcher ),summarise,count=length(Country))
# add acronyms
df = merge(countMembersESR, coord, by="Country")
df$Early.Stage.Researcher<-ifelse(df$Early.Stage.Researcher=='Yes','ESR','Non-ESR') 
# revert melt to plot data using mapPies and replace NAN with 0
df_reverted <- dcast(df, Country ~ Early.Stage.Researcher, value.var='count')
df_reverted[is.na(df_reverted)]<-0 #is.na df, is.nan matrix//optional
df = merge(df_reverted, coord, by="Country")

# plot pie charts
mapPies(df, nameX="Lon", nameY="Lat", nameZs=c('Non-ESR', 'ESR'), zColours=c('indianred2', 'lightblue3'), symbolSize =1 ,ratio = 1, mapRegion='europe', addSizeLegend = TRUE, addCatLegend = TRUE  , oceanCol = "white", landCol = "grey60",borderCol = "white" )

# plot stacked bars

mapBars(df , nameX="Lon", nameY="Lat",nameZs=c('Non-ESR', 'ESR'), zColours=c('indianred2', 'lightblue3'), barWidth = 1, barOrient = 'vert', barRelative = TRUE, ratio = 1, mapRegion='europe',addCatLegend = TRUE, addSizeLegend = TRUE, symbolSize = 3 , maxZVal=40, xlim=NA, ylim=NA, oceanCol = "white", landCol = "grey60",borderCol = "white", add=FALSE, main='', lwd=0.5, lwdSymbols=1) 

#map only participants
          
# plot pie charts
countMembersGender<- ddply(db,.(Country, Gender),summarise,count=length(Country))
# add acronyms
df = merge(countMembersGender, coord, by="Country")
df_reverted <- dcast(df, Country ~ Gender, value.var='count')
df_reverted[is.na(df_reverted)]<-0 #is.na df, is.nan matrix//optional
df = merge(df_reverted, coord, by="Country")
mapPies(df, nameX="Lon", nameY="Lat", nameZs=c('F', 'M'), zColours=c('indianred2', 'lightblue3'), symbolSize =1 ,ratio =1, mapRegion='europe', addSizeLegend = TRUE, addCatLegend = TRUE  , oceanCol = "white", landCol = "grey60",borderCol = "white" )        
```



